Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-07 article/article.Rmd
Commit 2024-06-07 15:12

\  
\

@@

An important aspect of the variability of solar radiation is its interaction with the
clouds. In general, clouds can attenuate a fraction  of solar irradiance, but under
certain conditions, can lead to  enhancement of the global horizontal irradiance
(GHI) reaching the ground. This effect can locally increase the observed GHI to
levels even higher than the expected clear-sky irradiance [see references therein].

Some of the proposed underling mechanisms of those enhancements, have been summarized
by @Gueymard2017, and include scattering on the edge of cumulus clouds or through
thin cirrus.  Further investigation with radiation transfer modeling methods and
observations have pointed as the prevailing mechanism, the forward Mie scattering
[@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015], through the clouds.
The overall phenomenon depends on different interactive factors, which includes cloud
thickness, constitution and type; and the relative position of the sun and the clouds
[@Gueymard2017; @Veerman2022].  As such, there are multiple contributing mechanisms
that are responsible for the observed irradiance enhancements.

On multiple sites, cloud enhancements have been reported, to be able to briefly exceed the
value of the solar constant, resulting of clear indexes above unit. A summary of
extreme enchantment cases (ECE) have been compiled by @Martins2022. There are also, some
practical implication of the cloud enchantments.  The intensity and duration of
enhancements can effect the efficiency and stability of photovoltaic power production
[@Lappalainen2020; @Jaervelae2020], and extreme enhancements cases, have the
potential to compromise the integrity of photovoltaic plants infrastructure
[@DoNascimento2019].  It has also been demonstrated, that these events can interfere
in the comparison of ground data and satellite observations [@Damiani2018]

<!--
Study of the mechanism has also been done with modeling of different cloud types and
atmospheric conditions.  @Gueymard2017; @Veerman2022
-->
<!--
Instruments respose ....
@Martins2022
-->

Methods of identification cloud enchantment events in the literature, usually include
the use of a simulated clear sky radiation as baseline, that is combined with an
appropriate threshold or some other statistical characteristics, and in some cases,
with visual methods with a sky cam [@Vamvakas2020; @Mol2023 and references therein].

<!-- our work -->
In this study, we evaluated the effects CE on the GHI by studding the occurrences, their intensity, and their duration in a
thirty-year period at the city of Thessaloniki.  We used modeled clear sky
irradiance, as a baseline to identify cloud enhancements.  We were able to determine
some trends of the phenomenon, it's Climatology, and some of their  general
characteristics. We weren't able to find a comparable study that provides trends for
similar long term dataset, as ours.  The recording of the GHI signal is the
mean of one-minute. Thus, the minimum resolution of CE events, in
this study is one minute.

>>>>

@@

An important aspect of the variability of solar radiation is its interaction with the
clouds. In general, clouds can attenuate a fraction  of solar irradiance, but under
certain conditions, can lead to  enhancement of the global horizontal irradiance
(GHI) reaching the ground. This effect can locally increase the observed GHI to
levels even higher than the expected clear-sky irradiance [@Cordero2023;
@Vamvakas2020; @CastillejoCuberos2020; @Vamvakas2020 and references therein].

Some of the proposed underling mechanisms of those enhancements, have been summarized
by @Gueymard2017; the most important being the scattering of radiation on the edges
of cumulus clouds.  It has been also suggested that enhancement of GHI can be
produced by thin cirrus clouds though refraction and scattering [@Thuillier2013].
Further investigation with radiative transfer modeling and observations pointed as
the prevailing mechanism, the strong forward Mie scattering through clouds of low
optical depth [@Pecenak2016; @Thuillier2013; @Yordanov2013; @Yordanov2015].  Overall,
enhancement event depend on different interactive factors, which include cloud
thickness, structure and type, and the relative position of the sun and the clouds
[@Gueymard2017; @Veerman2022].

On multiple sites, cloud enhancements (CE) have been reported to be able to briefly
exceed the value of the solar constant, resulting of clearness indices above unit. A
summary of extreme enchantment cases (ECE) has been compiled by @Martins2022. There
are also; some practical implications of the cloud enchantments.  The intensity and
duration of enhancements can effect the efficiency and stability of photovoltaic
power production [@Lappalainen2020; @Jaervelae2020]; while ECEs have the potential to
compromise the integrity of photovoltaic plants infrastructure [@DoNascimento2019].
It has also been demonstrated, that these events can interfere in the comparison of
ground-based and satellite observations [@Damiani2018]

<!--
Study of the mechanism has also been done with modeling of different cloud types and
atmospheric conditions.  @Gueymard2017; @Veerman2022
-->
<!--
Instruments respose ....
@Martins2022
-->
Methods of identification of CE events usually include the use of simulated clear
sky irradiance as baseline, that is combined with an appropriate threshold or some
other statistical characteristics, and in some cases, with visual inspection of sky
camera images [@Vamvakas2020; @Mol2023 and references therein].

<!-- our work -->
In this study, we evaluate the effects CE on GHI by investigating their frequency of
occurrence, intensity, and duration in a thirty-year period of GHI observations at
Thessaloniki, Greece.  We used modeled clear sky irradiance, as a baseline to
identify cloud enhancements.  We were able to determine some trends of the
phenomenon, it's Climatology, and some of their  general characteristics. We weren't
able to find a comparable study that provides trends for similar long term dataset,
as ours.  The recording of the GHI signal is the mean of one-minute. Thus, the
minimum resolution of CE events, in this study is one minute.

### 2024-06-07 article/article.tex
Commit 2024-06-07 15:12

~ ~

@@

An important aspect of the variability of solar radiation is its
interaction with the clouds. In general, clouds can attenuate a fraction
of solar irradiance, but under certain conditions, can lead to
enhancement of the global horizontal irradiance (GHI) reaching the
ground. This effect can locally increase the observed GHI to levels even
higher than the expected clear-sky irradiance {[}see references
therein{]}.

Some of the proposed underling mechanisms of those enhancements, have
been summarized by \citet{Gueymard2017}, and include scattering on the
edge of cumulus clouds or through thin cirrus. Further investigation
with radiation transfer modeling methods and observations have pointed
as the prevailing mechanism, the forward Mie scattering
\citep{Pecenak2016, Thuillier2013, Yordanov2013, Yordanov2015}, through
the clouds. The overall phenomenon depends on different interactive
factors, which includes cloud thickness, constitution and type; and the
relative position of the sun and the clouds
\citep{Gueymard2017, Veerman2022}. As such, there are multiple
contributing mechanisms that are responsible for the observed irradiance
enhancements.

On multiple sites, cloud enhancements have been reported, to be able to
briefly exceed the value of the solar constant, resulting of clear
indexes above unit. A summary of extreme enchantment cases (ECE) have
been compiled by \citet{Martins2022}. There are also, some practical
implication of the cloud enchantments. The intensity and duration of
enhancements can effect the efficiency and stability of photovoltaic
power production \citep{Lappalainen2020, Jaervelae2020}, and extreme
enhancements cases, have the potential to compromise the integrity of
photovoltaic plants infrastructure \citep{DoNascimento2019}. It has also
been demonstrated, that these events can interfere in the comparison of
ground data and satellite observations \citep{Damiani2018}

Methods of identification cloud enchantment events in the literature,
usually include the use of a simulated clear sky radiation as baseline,
that is combined with an appropriate threshold or some other statistical
characteristics, and in some cases, with visual methods with a sky cam
\citep[ and references therein]{Vamvakas2020, Mol2023}.

In this study, we evaluated the effects CE on the GHI by studding the
occurrences, their intensity, and their duration in a thirty-year period
at the city of Thessaloniki. We used modeled clear sky irradiance, as a
baseline to identify cloud enhancements. We were able to determine some
trends of the phenomenon, it's Climatology, and some of their general
characteristics. We weren't able to find a comparable study that
provides trends for similar long term dataset, as ours. The recording of
the GHI signal is the mean of one-minute. Thus, the minimum resolution
of CE events, in this study is one minute.

>>>>

@@

An important aspect of the variability of solar radiation is its
interaction with the clouds. In general, clouds can attenuate a fraction
of solar irradiance, but under certain conditions, can lead to
enhancement of the global horizontal irradiance (GHI) reaching the
ground. This effect can locally increase the observed GHI to levels even
higher than the expected clear-sky irradiance \citep[ and references
therein]{Cordero2023, Vamvakas2020, CastillejoCuberos2020, Vamvakas2020}.

Some of the proposed underling mechanisms of those enhancements, have
been summarized by \citet{Gueymard2017}; the most important being the
scattering of radiation on the edges of cumulus clouds. It has been also
suggested that enhancement of GHI can be produced by thin cirrus clouds
though refraction and scattering \citep{Thuillier2013}. Further
investigation with radiative transfer modeling and observations pointed
as the prevailing mechanism, the strong forward Mie scattering through
clouds of low optical depth
\citep{Pecenak2016, Thuillier2013, Yordanov2013, Yordanov2015}. Overall,
enhancement event depend on different interactive factors, which include
cloud thickness, structure and type, and the relative position of the
sun and the clouds \citep{Gueymard2017, Veerman2022}.

On multiple sites, cloud enhancements (CE) have been reported to be able
to briefly exceed the value of the solar constant, resulting of
clearness indices above unit. A summary of extreme enchantment cases
(ECE) has been compiled by \citet{Martins2022}. There are also; some
practical implications of the cloud enchantments. The intensity and
duration of enhancements can effect the efficiency and stability of
photovoltaic power production \citep{Lappalainen2020, Jaervelae2020};
while ECEs have the potential to compromise the integrity of
photovoltaic plants infrastructure \citep{DoNascimento2019}. It has also
been demonstrated, that these events can interfere in the comparison of
ground-based and satellite observations \citep{Damiani2018}

Methods of identification of CE events usually include the use of
simulated clear sky irradiance as baseline, that is combined with an
appropriate threshold or some other statistical characteristics, and in
some cases, with visual inspection of sky camera images \citep[ and
references therein]{Vamvakas2020, Mol2023}.

In this study, we evaluate the effects CE on GHI by investigating their
frequency of occurrence, intensity, and duration in a thirty-year period
of GHI observations at Thessaloniki, Greece. We used modeled clear sky
irradiance, as a baseline to identify cloud enhancements. We were able
to determine some trends of the phenomenon, it's Climatology, and some
of their general characteristics. We weren't able to find a comparable
study that provides trends for similar long term dataset, as ours. The
recording of the GHI signal is the mean of one-minute. Thus, the minimum
resolution of CE events, in this study is one minute.
